### 2013-10-05 chi2014/qualitative.tex
revised first half

Another type of riffing is \emph{exhaustive mutation}. Under this strategy, a participant repeats a response nearly verbatim many times, each time replacing a single word or concept in such a way that no new ideas are formed. For example:

@@

Within and across these strategies, there are a few repeated phenomena.
Some participants \emph{pair} their riffs. These participants  often riff on old ideas but never produce more than two versions of each idea. This may represent a desire to generate more ideas to meet the task expectations, but a trepitation that repeated ideas are less satisfying than completely unique ones.

Another phenomenon is \emph{linguistic riffing}. Some participants seem to use common sentence structure as queues when generating ideas. For example:

@@

Note the distinction from exhaustive mutation. In the exhaustive mutation example above, instances using the same language were interchangeable.
In this example, while language is re-used, each instance is a new idea.

>>>>

Another type of riffing is \emph{repeat riffing}. Under this strategy, a participant produces multiple reponses with only slight differences between them. For example:

\begin{itemize}
    \item recycle to make better MP3/ipod players
    \item use the circuits to for the ipod/MP3 to power other things that are more recent
\end{itemize}

In this case, the participant is providing the same idea (namely, creating new electronic devices from the parts) twice.

@@

Within and across these strategies, there are a few repeated phenomena.
Some participants \emph{pair} their riffs. These participants  often riff on old ideas but never produce more than two versions of each idea. For example, paired exhaustive riffing from a participant:

\begin{itemize}
\item TODO
\item TODO
\end{itemize}

Another phenomenon is \emph{language repitition}. Some participants seem to use common sentence structure as queues when generating ideas. For example:

@@

In this example, while language is re-used, each instance is a new idea.
However, language repitition is especially common in repeat riffing, as this example shows:
